Sulfur Dioxide at Water's Surface

### 2011-02-18 EquilibratedOrientation.tex
more on water orientation results

The results of the analyses for \wat~are shown in figure \ref{fig:water-orientation} for both the neat-water and saturated systems. In both systems an orientational preference is found at the slab surfaces where the water is in contact with the gas phase, or the surface \suldiox~molecules. %The bisector tilt concentrates around $\cos(\theta)=0$ within the first few\angs of the surface, and then the distribution becomes isotropic further into the water bulk. As the tilt nears $\cos(\theta)=0$ the \wat~bisector lies within the plane of the surface indicating a water orientation either flat on the surface, or with some amount of ``twist'' sending the OH bonds in towards, or out of the bulk. The value of $\phi$ determines the ``twist'' in this case. Both systems show a peak in the distributions around $\cos(\phi)=1$ at the water surfaces. This results from an orientation of the water's y-axis (normal to the molecular plane) aligned perpendicular to the plane of the water surface.

@@

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/waterorientationsmall.png}
		\caption{Molecular orientation histograms of \wat~throughout the surface equilibrated systems. The top surface is located at a distance of 0 with negative positions in the bulk of the slab. The bottom slab surface is approx. 30\angs below the top surface. Shown are the angle distributions for $\theta$ (left column) and $\phi$ (right column) in both the neat-\wat~system (top row) and the saturated system (bottom row). Dark blue regions are void of water molecules above the top and below the bottom surfaces.}
		\label{fig:water-orientation}
	\end{center}
\end{figure}

>>>>

The results of the analyses for \wat~are shown in figure \ref{fig:water-orientation} for both the neat-water and saturated systems. In both systems an orientational preference is found at the slab surfaces where the water is in contact with the gas phase, or the surface \suldiox~molecules. The histograms are arranged with the plots of $\theta$ on the left and $\phi$ on the right columns, and the results for the neat-water and saturated systems are in the top and bottom rows, respectively. %The bisector tilt concentrates around $\cos(\theta)=0$ within the first few\angs of the surface, and then the distribution becomes isotropic further into the water bulk. As the tilt nears $\cos(\theta)=0$ the \wat~bisector lies within the plane of the surface indicating a water orientation either flat on the surface, or with some amount of ``twist'' sending the OH bonds in towards, or out of the bulk. The value of $\phi$ determines the ``twist'' in this case. Both systems show a peak in the distributions around $\cos(\phi)=1$ at the water surfaces. This results from an orientation of the water's y-axis (normal to the molecular plane) aligned perpendicular to the plane of the water surface.
The histograms show overall similarities in their shapes and distributions indicating that the presence of a saturated layer of adsorbed \suldiox~molecules alters the water orientation, but not necessarily the depth of the interface.

@@

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/h2o-angles/h2oangles.png}
		\caption{Molecular orientation histograms of \wat~throughout the surface equilibrated systems. The top surface is located at a distance of 0 with negative positions in the bulk of the slab. The bottom slab surface is approx. 30\angs below the top surface. Shown are the angle distributions for $\theta$ (left column) and $\phi$ (right column) in both the neat-\wat~system (top row) and the saturated system (bottom row). Dark blue regions are void of water molecules above the top and below the bottom surfaces.}
		\label{fig:water-orientation}
	\end{center}
\end{figure}
